---
title: "Evaluating ORES Models"
author: "Avner Kantor"
date: "3.4.2016"
output: html_document
---

**The Objective Revision Evaluation Service (ORES)** is a web service running in Wikimedia Labs that provides machine learning as a service for Wikimedia Projects. (<https://ores.wmflabs.org/>). You can read more [here](http://socio-technologist.blogspot.co.il/2015/10/ores-hacking-social-structures-by.html>).

The damage model was trained on human judgement to predict damaging edits. Remember that not all damaging edits are bad-faith.(<https://meta.wikimedia.org/wiki/ORES/damaging>) 

We explored the bias that ORES' damage detection models have against anonymous editors in Wikipedia. We did a statistical analysis to show that the bias is extreme and then changed our modeling strategy to minimize the bias re-measured the effects.

Thanks Aaron for the supervision!

### V2 Model - Damaging
Example: https://ores.wmflabs.org/v2/scores/enwiki/damaging/623818349/

```{r, eval=FALSE}
# Download revs_id
library(jsonlite)

document <- fromJSON("http://labels.wmflabs.org/campaigns/enwiki/4/?tasks")

# Find revs_is.labels.damaging
revs_id<- document$tasks$data$rev_id
damagings<- sapply(1:20000, function(x) document$tasks$labels[[x]]$data$damaging)

# Find damaging predictions
df<-as.data.frame(cbind(revs_id, damagings))
dfFalse<-select(filter(df, damagings!="TRUE"), revs_id)
dfTrue<-select(filter(df, damagings=="TRUE"), revs_id)

# Get Damaging Probabilities
getStats <- function(id) {
  rdTrue <- fromJSON(paste0("https://ores.wmflabs.org/v2/scores/enwiki/damaging/", id, "/?feature.is_anon=true"))
  rdFalse<-fromJSON(paste0("https://ores.wmflabs.org/v2/scores/enwiki/damaging/", id, "/?feature.is_anon=false"))
  
  rdTruePredictionTrue<-rdTrue$scores$enwiki$damaging$scores[[1]]$probability$true
  rdTruePredictionFalse<-rdFalse$scores$enwiki$damaging$scores[[1]]$probability$true
  
  return(list(rdTruePredictionTrue, rdTruePredictionFalse))
}

# Test  Model - Prediction is False
anonFalseModel<-sapply(1:500, function(x) getStats(dfFalse[x,]))
```

```{r, echo=FALSE}
load("data/anonFalseModel.rda")
```

```{r, echo=TRUE, message=FALSE, warning=FALSE}
### Manipulating
library(dplyr)
library(reshape2)

anonFalseModelDF<-t(anonFalseModel)
colnames(anonFalseModelDF)<-c("anon_true", "anon_false")
anonFalseModelDF<-as.data.frame(anonFalseModelDF)
anonFalseModelDFManipulated<-melt(lapply(anonFalseModelDF, unlist))

### PlotFalse
library(ggplot2)

ggplot(anonFalseModelDFManipulated, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is false", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

###Calculate the difference
anonFalseModelDF$difference<-as.numeric(as.character(anonFalseModelDF$anon_true))-as.numeric(as.character(anonFalseModelDF$anon_false))
anonFalseModelDF<-anonFalseModelDF[, c("anon_true", "anon_false", "difference")]
anonFalseModelDFManipulated2<-melt(lapply(anonFalseModelDF, unlist))

### PlotTrue2
ggplot(anonFalseModelDFManipulated2, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is false+difference", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")
```

Now, let's calculate the true probabilities in the same way.

```{r, echo=FALSE}
load("data/anonTrueModel.rda")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
### Manipulating
anonTrueModelDF<-t(anonTrueModel)
colnames(anonTrueModelDF)<-c("anon_true", "anon_false")
anonTrueModelDF<-as.data.frame(anonTrueModelDF)
anonTrueModelDFManipulated<-melt(lapply(anonTrueModelDF, unlist))

### PlotTrue
ggplot(anonTrueModelDFManipulated, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is true", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

###Calculate the difference
anonTrueModelDF$difference<-as.numeric(as.character(anonTrueModelDF$anon_true))-as.numeric(as.character(anonTrueModelDF$anon_false))
anonTrueModelDF<-anonTrueModelDF[, c("anon_true", "anon_false", "difference")]
anonTrueModelDFManipulated2<-melt(lapply(anonTrueModelDF, unlist))

### PlotTrue2
ggplot(anonTrueModelDFManipulated2, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is true+difference", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

```

### The New Model - Damaging
Example: https://ores-newmodels.wmflabs.org/v2/scores/enwiki/damaging/623818349/
```{r, echo=FALSE}
load("data/anonFalseNewModel.rda")
load("data/anonTrueNewModel.rda")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
### Manipulating
anonFalseNewModelDF<-t(anonFalseNewModel)
colnames(anonFalseNewModelDF)<-c("anon_true", "anon_false")
anonFalseNewModelDF<-as.data.frame(anonFalseNewModelDF)
anonFalseNewModelDFManipulated<-melt(lapply(anonFalseNewModelDF, unlist))

### PlotFalse
ggplot(anonFalseNewModelDFManipulated, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is false", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

### Manipulating
anonFalseNewModelDF$difference<-as.numeric(as.character(anonFalseNewModelDF$anon_true))-as.numeric(as.character(anonFalseNewModelDF$anon_false))
anonFalseNewModelDF<-anonFalseNewModelDF[, c("anon_true", "anon_false", "difference")]
anonTrueNewModelDFManipulated2<-melt(lapply(anonFalseNewModelDF, unlist))

### PlotFalse2
ggplot(anonTrueNewModelDFManipulated2, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is false+difference", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

### Manipulating
anonTrueNewModelDF<-t(anonTrueNewModel)
colnames(anonTrueNewModelDF)<-c("anon_true", "anon_false")
anonTrueNewModelDF<-as.data.frame(anonTrueNewModelDF)
anonTrueNewModelDFManipulated<-melt(lapply(anonTrueNewModelDF, unlist))

### PlotTrue
ggplot(anonTrueNewModelDFManipulated, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is true", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

###Calculate the difference
anonTrueNewModelDF$difference<-as.numeric(as.character(anonTrueNewModelDF$anon_true))-as.numeric(as.character(anonTrueNewModelDF$anon_false))
anonTrueNewModelDF<-anonTrueNewModelDF[, c("anon_true", "anon_false", "difference")]
anonTrueNewModelDFManipulated2<-melt(lapply(anonTrueNewModelDF, unlist))

### PlotTrue2
ggplot(anonTrueNewModelDFManipulated2, aes(x=value)) + 
  geom_density(aes(group=L1, colour=L1, fill=L1), alpha=0.3) +
  labs(title="ORES damaging prediction is true+difference", x="N=500") + 
  geom_vline(xintercept = c(0.8, 0.87, 0.94),  colour="green", linetype = "longdash")

```
